\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Problem Set 1}
\author{Caden Finley}
\date{January 25, 2023}
\begin{document}
\maketitle


\section{Introduction}

Data Science is an expanding field right now in terms of education and professional work. For me, this class seemed interesting to learn some new skills to stand out in the workforce. Understanding more about Machine Learning as well as the different software will be extremely useful for the future. Many of the applications of the various programming languages could prove very beneficial in the line of work I wish to be in. Right now, I am looking into investment banking and part of the work you do in that profession is modeling. If I could use this skills from this class to make more detailed models, I believe this would separate from most of the competition. Hopefully, I can do a project related to investment banking that involves some modeling as well as coding. This would involve taking financial data from various companies and creating efficient ways to display the information using either SQL or R studio. I would utilize the various functions and applications of these software to create a cohesive project that meets the requirements of the course. Some of my goals include being proficient in SQL and to learn how to apply aspects of this class to the finance world. Specifically, if I can make more efficient models for a DCF analysis or Leveraged Buyout Model. The knowledge from this course would most likely give me the tools to refine and better these models. As far as graduation goes, I want to move up to New York and work for a big investment banking firm there. There is a lot of opportunity to develop professionally as well as personally. This course will give a little bit of insight to other professions as well, should I choose to change my career path. Numerous skills go into understanding and implementing data science into a work profession, so that is why I want to take the most advantage of this course as I can.  

\section{Equation}

\begin{displaymath}
\end{displaymath}

\[ a^2 + b^2 = c^2 \]


\end{document}